Cross Language Similar Sentence Detection

### 2013-12-08 article/clarticle/article-draft.tex
Article updates

\numberofauthors{3}

@@

\section{Locality \\ Sensitive Hashing}

In order to measure document similarity we use a common LSH technique known as MinHash (\cite{broder:resemblance}). A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$. For each input feature set $S$ (in our case a set of words or translated words) a vector $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family is produced. The signature on a document $d$ is represented as a vector of $K$ minhashes, chosen from the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes. In order to minimize false negatives we apply a technique sometimes known as ``banding'' \cite{ullman:massive} where multiple signatures are produced for each input document.

@@

>>>>

\numberofauthors{1}

@@

Following Ture, et. al 2011 [ref], we use parallel German and English texts from the Europarl corpus, which contains proceedings from the European Parliament (1996— 2009), to compare empirically the performance of cross-language minhashing to signature matching on a machine translated text. (Here our machine translation tool is the Google Translate web tool.)  In the first case we translat each German sentence into English and then process the resulting sentences using a straightforward minhash signature algorithm. In the second case, we use our sampling approach to create a number of possible documents, each which gets input into the minhash algorithm. We then calculated Jaccard similarity for the translated document pairs. Figure \ref{mtclircompare} shows the two distributions of Jaccard similarity scores for each document set, comparing matches and non-matches. We can see that the sampling approach performs similarity to the translation approach, finding documents that are similar under machine translation nearly as well as if we had compared the translated texts.

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{clirhist.pdf}
\includegraphics[width=3.5in, keepaspectratio = true]{transhist.pdf}
\caption{Histograms of Europarl Matches by Jaccard Similarity for both CLIR and translation technique.}
\label{mtclircompare}
\end{figure}

\section{Signature Techniques}

In order to measure document similarity we use a common signature technique known as minhash (\cite{broder:resemblance}). A minhash signature on a text document is calculated using a parametrized family of hash functions $F_i$, $1 \le i \le N$. For each input feature set $S$ (in our case a set of words or translated words) a vector $\{min_{s \in S}(F_i(s)\}$ of minimum hashes over the hash family is produced. The signature on a document $d$ is represented as a vector of $K$ minhashes, chosen from the set $\{min_{s \in S}(F_i(s)\}$ of minimum hashes. In order to minimize false negatives we apply a technique sometimes known as ``banding'' \cite{ullman:massive} where multiple signatures are produced for each input document.

In order to compare the effectiveness of our cross-language minhashing approach we compare the technique to a second signature technique, random projections as described in Ture, et. al 2011 [ref].

@@

In order to run our tests we use the Random Projections code made available as part of the Ivory library (link).
